---
title: "Notebook_DescriptiveAnalysis"
output: html_notebook
---
Load scripts
```{r}
library(here)
library(survey)
library(tidyverse)
library(ggplot2)
```
Use the "for analysis" file created with the data wrangling script
```{r}
path_to_data <- here("Data", "WGM_for_analysis_rds.rds")
WGM_an <- readRDS(path_to_data)
```
Set overall survey weights
```{r}
WGM_anSurveyDesign <- svydesign(
  ids = ~1,
  weights =  WGM_an$wgt, 
  data = WGM_an
)
```
##Uganda
How many total respondents 
```{r}
nrow(filter(WGM_an, WP5 == "Uganda"))
```
How many respondents in country who have children and know about vaccines
```{r}
nrow(filter(WGM_an, WP5 == "Uganda" & Q27 == "Yes" & Q23 == "Yes"))
```
Filter survey weights to country
```{r}
Uganda_Design <- subset(WGM_anSurveyDesign, 
                        WP5 == "Uganda" &
                        Q27 == "Yes" &
                        Q23 == "Yes"
                        )
```
Age 
```{r}
Age_est_UG <- data.frame(svymean(~AgeCategories, Uganda_Design, na.rm= TRUE))
Age_conf_UG <- confint(svymean(~AgeCategories, Uganda_Design, na.rm= TRUE))
Age_frame_UG <- data.frame(estimate = Age_est_UG, 
                        CI = Age_conf_UG)
Age_frame_UG <- Age_frame_UG*100
Age_frame_UG$estimate.mean <- round(Age_frame_UG$estimate.mean, 1)
Age_est_labs <- c("15-29", "30-49", "50+")
Age_frame_UG <- cbind(Age_frame_UG, Age_est_labs)

Ageplot_UG <- ggplot(Age_frame_UG,
       aes(x=Age_est_labs, y=estimate.mean)) +
       geom_col(fill="cornflowerblue")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Age Cohort")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Ageplot_UG)
```
Gender
```{r}
Gender_est_UG <- data.frame(svymean(~Gender, Uganda_Design, na.rm= TRUE))
Gender_conf_UG <- confint(svymean(~Gender, Uganda_Design, na.rm= TRUE))
Gender_frame_UG <- data.frame(estimate = Gender_est_UG, CI = Gender_conf_UG)
Gender_frame_UG <- Gender_frame_UG*100
Gender_frame_UG$estimate.mean <- round(Gender_frame_UG$estimate.mean, 1)
Gender_est_labs <- c("Male", "Female")
Gender_frame_UG <- cbind(Gender_frame_UG, Gender_est_labs)

Genderplot_UG <- ggplot(Gender_frame_UG,
       aes(x=Gender_est_labs, y=estimate.mean)) +
       geom_col(fill="cornflowerblue")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Gender")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Genderplot_UG)
```
Education
```{r}
Education_est_UG <- data.frame(svymean(~Education, Uganda_Design, na.rm= TRUE))
Education_conf_UG <- confint(svymean(~Education, Uganda_Design, na.rm= TRUE))
Education_frame_UG <- data.frame(estimate = Education_est_UG, 
                        CI = Education_conf_UG)
Education_frame_UG <- Education_frame_UG*100
Education_frame_UG$estimate.mean <- round(Education_frame_UG$estimate.mean, 1)
Education_est_labs <- c("Primary", "Secondary", "Tertiary")
Education_frame_UG <- cbind(Education_frame_UG, Education_est_labs)

Educationplot_UG <- ggplot(Education_frame_UG,
       aes(x=Education_est_labs, y=estimate.mean)) +
       geom_col(fill="cornflowerblue")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), 
            position = position_dodge(width = 1),
            vjust = -2,
            size=3)+ 
  labs(y=" ", x=" ")+
  ylim(0,100)+
  ggtitle("Education")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Educationplot_UG)
```
Setting 
```{r}
Urban_Rural_est_UG <- data.frame(svymean(~Urban_Rural, Uganda_Design, na.rm= TRUE))
Urban_Rural_conf_UG <- confint(svymean(~Urban_Rural, Uganda_Design, na.rm= TRUE))
Urban_Rural_frame_UG <- data.frame(estimate = Urban_Rural_est_UG, 
                        CI = Urban_Rural_conf_UG)
Urban_Rural_frame_UG <- Urban_Rural_frame_UG*100
Urban_Rural_frame_UG$estimate.mean <- round(Urban_Rural_frame_UG$estimate.mean, 1)
Urban_Rural_est_labs <- c("Rural or small town", "City or suburb")
Urban_Rural_frame_UG <- cbind(Urban_Rural_frame_UG, Urban_Rural_est_labs)

Urban_Ruralplot_UG <- ggplot(Urban_Rural_frame_UG,
       aes(x=Urban_Rural_est_labs, y=estimate.mean)) +
       geom_col(fill="cornflowerblue")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean),  position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Setting")+
  theme_classic()+
  ylim(0,120)+
  theme(plot.title = element_text(size = 12))
print(Urban_Ruralplot_UG)
```
Income
```{r}
Household_Income_est_UG <- data.frame(svymean(~Household_Income, Uganda_Design, na.rm= TRUE))
Household_Income_conf_UG <- confint(svymean(~Household_Income, Uganda_Design, na.rm= TRUE))
Household_Income_frame_UG <- data.frame(estimate = Household_Income_est_UG, 
                        CI = Household_Income_conf_UG)
Household_Income_frame_UG <- Household_Income_frame_UG*100
Household_Income_frame_UG$estimate.mean <- round(Household_Income_frame_UG$estimate.mean, 1)
Household_Income_est_labs <- c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%")
Household_Income_frame_UG <- cbind(Household_Income_frame_UG, Household_Income_est_labs)
Household_Income_frame_UG$Household_Income_est_labs <- factor(Household_Income_frame_UG$Household_Income_est_labs, level = c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%"))
levels(Household_Income_frame_UG$Household_Income_est_labs) <- gsub(" ", "\n", levels(Household_Income_frame_UG$Household_Income_est_labs))

Household_Incomeplot_UG <- ggplot(Household_Income_frame_UG,
       aes(x=Household_Income_est_labs, y=estimate.mean)) +
       geom_col(fill="cornflowerblue")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Income")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Household_Incomeplot_UG)
```
Vaccination
```{r}
svymean(~Q28, Uganda_Design, na.rm= TRUE)
confint(svymean(~Q28, Uganda_Design, na.rm= TRUE))
```
Multiplot function
```{r}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```
Put plots together 
```{r}
UG_plots <- multiplot(Ageplot_UG, Genderplot_UG, Educationplot_UG, Urban_Ruralplot_UG, Household_Incomeplot_UG, cols=2)
```
## Chad
How many total respondents 
```{r}
nrow(filter(WGM_an, WP5 == "Chad"))
```
How many respondents in country who have children and know about vaccines
```{r}
nrow(filter(WGM_an, WP5 == "Chad" & Q27 == "Yes" & Q23 == "Yes"))
```
Filter survey weights to country
```{r}
Chad_Design <- subset(WGM_anSurveyDesign, 
                        WP5 == "Chad" &
                        Q27 == "Yes" &
                        Q23 == "Yes"
                        )
```
Age 
```{r}
Age_est_CH <- data.frame(svymean(~AgeCategories, Chad_Design, na.rm= TRUE))
Age_conf_CH <- confint(svymean(~AgeCategories, Chad_Design, na.rm= TRUE))
Age_frame_CH <- data.frame(estimate = Age_est_CH, 
                        CI = Age_conf_CH)
Age_frame_CH <- Age_frame_CH*100
Age_frame_CH$estimate.mean <- round(Age_frame_CH$estimate.mean, 1)
Age_est_labs <- c("15-29", "30-49", "50+")
Age_frame_CH <- cbind(Age_frame_CH, Age_est_labs)

Ageplot_CH <- ggplot(Age_frame_CH,
       aes(x=Age_est_labs, y=estimate.mean)) +
       geom_col(fill="lightsteelblue2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Age Cohort")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Ageplot_CH)
```
Gender
```{r}
Gender_est_CH <- data.frame(svymean(~Gender, Chad_Design, na.rm= TRUE))
Gender_conf_CH <- confint(svymean(~Gender, Chad_Design, na.rm= TRUE))
Gender_frame_CH <- data.frame(estimate = Gender_est_CH, CI = Gender_conf_CH)
Gender_frame_CH <- Gender_frame_CH*100
Gender_frame_CH$estimate.mean <- round(Gender_frame_CH$estimate.mean, 1)
Gender_est_labs <- c("Male", "Female")
Gender_frame_CH <- cbind(Gender_frame_CH, Gender_est_labs)

Genderplot_CH <- ggplot(Gender_frame_CH,
       aes(x=Gender_est_labs, y=estimate.mean)) +
       geom_col(fill="lightsteelblue2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Gender")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Genderplot_CH)
```
Education
```{r}
Education_est_CH <- data.frame(svymean(~Education, Chad_Design, na.rm= TRUE))
Education_conf_CH <- confint(svymean(~Education, Chad_Design, na.rm= TRUE))
Education_frame_CH <- data.frame(estimate = Education_est_CH, 
                        CI = Education_conf_CH)
Education_frame_CH <- Education_frame_CH*100
Education_frame_CH$estimate.mean <- round(Education_frame_CH$estimate.mean, 1)
Education_est_labs <- c("Primary", "Secondary", "Tertiary")
Education_frame_CH <- cbind(Education_frame_CH, Education_est_labs)

Educationplot_CH <- ggplot(Education_frame_CH,
       aes(x=Education_est_labs, y=estimate.mean)) +
       geom_col(fill="lightsteelblue2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), 
            position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ylim(0,120)+
  ggtitle("Education")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Educationplot_CH)
```
Setting 
```{r}
Urban_Rural_est_CH <- data.frame(svymean(~Urban_Rural, Chad_Design, na.rm= TRUE))
Urban_Rural_conf_CH <- confint(svymean(~Urban_Rural, Chad_Design, na.rm= TRUE))
Urban_Rural_frame_CH <- data.frame(estimate = Urban_Rural_est_CH, 
                        CI = Urban_Rural_conf_CH)
Urban_Rural_frame_CH <- Urban_Rural_frame_CH*100
Urban_Rural_frame_CH$estimate.mean <- round(Urban_Rural_frame_CH$estimate.mean, 1)
Urban_Rural_est_labs <- c("Rural or small town", "City or suburb")
Urban_Rural_frame_CH <- cbind(Urban_Rural_frame_CH, Urban_Rural_est_labs)

Urban_Ruralplot_CH <- ggplot(Urban_Rural_frame_CH,
       aes(x=Urban_Rural_est_labs, y=estimate.mean)) +
       geom_col(fill="lightsteelblue2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean),  position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Setting")+
  theme_classic()+
  ylim(0,120)+
  theme(plot.title = element_text(size = 12))
print(Urban_Ruralplot_CH)
```
Income
```{r}
Household_Income_est_CH <- data.frame(svymean(~Household_Income, Chad_Design, na.rm= TRUE))
Household_Income_conf_CH <- confint(svymean(~Household_Income, Chad_Design, na.rm= TRUE))
Household_Income_frame_CH <- data.frame(estimate = Household_Income_est_CH, 
                        CI = Household_Income_conf_CH)
Household_Income_frame_CH <- Household_Income_frame_CH*100
Household_Income_frame_CH$estimate.mean <- round(Household_Income_frame_CH$estimate.mean, 1)
Household_Income_est_labs <- c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%")
Household_Income_frame_CH <- cbind(Household_Income_frame_CH, Household_Income_est_labs)
Household_Income_frame_CH$Household_Income_est_labs <- factor(Household_Income_frame_CH$Household_Income_est_labs, level = c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%"))
levels(Household_Income_frame_CH$Household_Income_est_labs) <- gsub(" ", "\n", levels(Household_Income_frame_CH$Household_Income_est_labs))

Household_Incomeplot_CH <- ggplot(Household_Income_frame_CH,
       aes(x=Household_Income_est_labs, y=estimate.mean)) +
       geom_col(fill="lightsteelblue2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Income")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Household_Incomeplot_CH)
```
Vaccination
```{r}
svymean(~Q28, Chad_Design, na.rm= TRUE)
confint(svymean(~Q28, Chad_Design, na.rm= TRUE))
```
Put plots together 
```{r}
CH_plots <- multiplot(Ageplot_CH, Genderplot_CH, Educationplot_CH, Urban_Ruralplot_CH, Household_Incomeplot_CH, cols=2)
```
## Brazil
How many total respondents 
```{r}
nrow(filter(WGM_an, WP5 == "Brazil"))
```
How many respondents in Uganda who have children and know about vaccines
```{r}
nrow(filter(WGM_an, WP5 == "Brazil" & Q27 == "Yes" & Q23 == "Yes"))
```
Filter survey weights to Uganda
```{r}
Brazil_Design <- subset(WGM_anSurveyDesign, 
                        WP5 == "Brazil" &
                        Q27 == "Yes" &
                        Q23 == "Yes"
                        )
```
Age 
```{r}
Age_est_BR <- data.frame(svymean(~AgeCategories, Brazil_Design, na.rm= TRUE))
Age_conf_BR <- confint(svymean(~AgeCategories, Brazil_Design, na.rm= TRUE))
Age_frame_BR <- data.frame(estimate = Age_est_BR, 
                        CI = Age_conf_BR)
Age_frame_BR <- Age_frame_BR*100
Age_frame_BR$estimate.mean <- round(Age_frame_BR$estimate.mean, 1)
Age_est_labs <- c("15-29", "30-49", "50+")
Age_frame_BR <- cbind(Age_frame_BR, Age_est_labs)

Ageplot_BR <- ggplot(Age_frame_BR,
       aes(x=Age_est_labs, y=estimate.mean)) +
       geom_col(fill="mediumpurple2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Age Cohort")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Ageplot_BR)
```
Gender
```{r}
Gender_est_BR <- data.frame(svymean(~Gender, Brazil_Design, na.rm= TRUE))
Gender_conf_BR <- confint(svymean(~Gender, Brazil_Design, na.rm= TRUE))
Gender_frame_BR <- data.frame(estimate = Gender_est_BR, CI = Gender_conf_BR)
Gender_frame_BR <- Gender_frame_BR*100
Gender_frame_BR$estimate.mean <- round(Gender_frame_BR$estimate.mean, 1)
Gender_est_labs <- c("Male", "Female")
Gender_frame_BR <- cbind(Gender_frame_BR, Gender_est_labs)

Genderplot_BR <- ggplot(Gender_frame_BR,
       aes(x=Gender_est_labs, y=estimate.mean)) +
       geom_col(fill="mediumpurple2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Gender")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Genderplot_BR)
```
Education
```{r}
Education_est_BR <- data.frame(svymean(~Education, Brazil_Design, na.rm= TRUE))
Education_conf_BR <- confint(svymean(~Education, Brazil_Design, na.rm= TRUE))
Education_frame_BR <- data.frame(estimate = Education_est_BR, 
                        CI = Education_conf_BR)
Education_frame_BR <- Education_frame_BR*100
Education_frame_BR$estimate.mean <- round(Education_frame_BR$estimate.mean, 1)
Education_est_labs <- c("Primary", "Secondary", "Tertiary")
Education_frame_BR <- cbind(Education_frame_BR, Education_est_labs)

Educationplot_BR <- ggplot(Education_frame_BR,
       aes(x=Education_est_labs, y=estimate.mean)) +
       geom_col(fill="mediumpurple2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), 
            position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ylim(0,100)+
  ggtitle("Education")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Educationplot_BR)
```
Setting 
```{r}
Urban_Rural_est_BR <- data.frame(svymean(~Urban_Rural, Brazil_Design, na.rm= TRUE))
Urban_Rural_conf_BR <- confint(svymean(~Urban_Rural, Brazil_Design, na.rm= TRUE))
Urban_Rural_frame_BR <- data.frame(estimate = Urban_Rural_est_BR, 
                        CI = Urban_Rural_conf_BR)
Urban_Rural_frame_BR <- Urban_Rural_frame_BR*100
Urban_Rural_frame_BR$estimate.mean <- round(Urban_Rural_frame_BR$estimate.mean, 1)
Urban_Rural_est_labs <- c("Rural or small town", "City or suburb")
Urban_Rural_frame_BR <- cbind(Urban_Rural_frame_BR, Urban_Rural_est_labs)

Urban_Ruralplot_BR <- ggplot(Urban_Rural_frame_BR,
       aes(x=Urban_Rural_est_labs, y=estimate.mean)) +
       geom_col(fill="mediumpurple2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean),  position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Setting")+
  theme_classic()+
  ylim(0,100)+
  theme(plot.title = element_text(size = 12))
print(Urban_Ruralplot_BR)
```
Income
```{r}
Household_Income_est_BR <- data.frame(svymean(~Household_Income, Brazil_Design, na.rm= TRUE))
Household_Income_conf_BR <- confint(svymean(~Household_Income, Brazil_Design, na.rm= TRUE))
Household_Income_frame_BR <- data.frame(estimate = Household_Income_est_BR, 
                        CI = Household_Income_conf_BR)
Household_Income_frame_BR <- Household_Income_frame_BR*100
Household_Income_frame_BR$estimate.mean <- round(Household_Income_frame_BR$estimate.mean, 1)
Household_Income_est_labs <- c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%")
Household_Income_frame_BR <- cbind(Household_Income_frame_BR, Household_Income_est_labs)
Household_Income_frame_BR$Household_Income_est_labs <- factor(Household_Income_frame_BR$Household_Income_est_labs, level = c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%"))
levels(Household_Income_frame_BR$Household_Income_est_labs) <- gsub(" ", "\n", levels(Household_Income_frame_BR$Household_Income_est_labs))

Household_Incomeplot_BR <- ggplot(Household_Income_frame_CH,
       aes(x=Household_Income_est_labs, y=estimate.mean)) +
       geom_col(fill="mediumpurple2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Income")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Household_Incomeplot_BR)
```
Vaccination
```{r}
svymean(~Q28, Brazil_Design, na.rm= TRUE)
confint(svymean(~Q28, Brazil_Design, na.rm= TRUE))
```
Put plots together 
```{r}
BR_plots <- multiplot(Ageplot_BR, Genderplot_BR, Educationplot_BR, Urban_Ruralplot_BR, Household_Incomeplot_BR, cols=2)
```
## Ethiopia
How many total respondents 
```{r}
nrow(filter(WGM_an, WP5 == "Ethiopia"))
```
How many respondents in country who have children and know about vaccines
```{r}
nrow(filter(WGM_an, WP5 == "Ethiopia" & Q27 == "Yes" & Q23 == "Yes"))
```
Filter survey weights to country
```{r}
Ethiopia_Design <- subset(WGM_anSurveyDesign, 
                        WP5 == "Ethiopia" &
                        Q27 == "Yes" &
                        Q23 == "Yes"
                        )
```
Age 
```{r}
Age_est_ET <- data.frame(svymean(~AgeCategories, Ethiopia_Design, na.rm= TRUE))
Age_conf_ET <- confint(svymean(~AgeCategories, Ethiopia_Design, na.rm= TRUE))
Age_frame_ET <- data.frame(estimate = Age_est_ET, 
                        CI = Age_conf_ET)
Age_frame_ET <- Age_frame_ET*100
Age_frame_ET$estimate.mean <- round(Age_frame_ET$estimate.mean, 1)
Age_est_labs <- c("15-29", "30-49", "50+")
Age_frame_ET <- cbind(Age_frame_ET, Age_est_labs)

Ageplot_ET <- ggplot(Age_frame_ET,
       aes(x=Age_est_labs, y=estimate.mean)) +
       geom_col(fill="honeydew2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Age Cohort")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Ageplot_ET)
```
Gender
```{r}
Gender_est_ET <- data.frame(svymean(~Gender, Ethiopia_Design, na.rm= TRUE))
Gender_conf_ET <- confint(svymean(~Gender, Ethiopia_Design, na.rm= TRUE))
Gender_frame_ET <- data.frame(estimate = Gender_est_ET, CI = Gender_conf_ET)
Gender_frame_ET <- Gender_frame_ET*100
Gender_frame_ET$estimate.mean <- round(Gender_frame_ET$estimate.mean, 1)
Gender_est_labs <- c("Male", "Female")
Gender_frame_ET <- cbind(Gender_frame_ET, Gender_est_labs)

Genderplot_ET <- ggplot(Gender_frame_ET,
       aes(x=Gender_est_labs, y=estimate.mean)) +
       geom_col(fill="honeydew2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Gender")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Genderplot_ET)
```
Education
```{r}
Education_est_ET <- data.frame(svymean(~Education, Ethiopia_Design, na.rm= TRUE))
Education_conf_ET <- confint(svymean(~Education, Ethiopia_Design, na.rm= TRUE))
Education_frame_ET <- data.frame(estimate = Education_est_ET, 
                        CI = Education_conf_ET)
Education_frame_ET <- Education_frame_ET*100
Education_frame_ET$estimate.mean <- round(Education_frame_ET$estimate.mean, 1)
Education_est_labs <- c("Primary", "Secondary", "Tertiary")
Education_frame_ET <- cbind(Education_frame_ET, Education_est_labs)

Educationplot_ET <- ggplot(Education_frame_ET,
       aes(x=Education_est_labs, y=estimate.mean)) +
       geom_col(fill="honeydew2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), 
            position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ylim(0,120)+
  ggtitle("Education")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Educationplot_ET)
```
Setting 
```{r}
Urban_Rural_est_ET <- data.frame(svymean(~Urban_Rural, Ethiopia_Design, na.rm= TRUE))
Urban_Rural_conf_ET <- confint(svymean(~Urban_Rural, Ethiopia_Design, na.rm= TRUE))
Urban_Rural_frame_ET <- data.frame(estimate = Urban_Rural_est_ET, 
                        CI = Urban_Rural_conf_ET)
Urban_Rural_frame_ET <- Urban_Rural_frame_ET*100
Urban_Rural_frame_ET$estimate.mean <- round(Urban_Rural_frame_ET$estimate.mean, 1)
Urban_Rural_est_labs <- c("Rural or small town", "City or suburb")
Urban_Rural_frame_ET <- cbind(Urban_Rural_frame_ET, Urban_Rural_est_labs)

Urban_Ruralplot_ET <- ggplot(Urban_Rural_frame_ET,
       aes(x=Urban_Rural_est_labs, y=estimate.mean)) +
       geom_col(fill="honeydew2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean),  position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Setting")+
  theme_classic()+
  ylim(0,120)+
  theme(plot.title = element_text(size = 12))
print(Urban_Ruralplot_ET)
```
Income
```{r}
Household_Income_est_ET <- data.frame(svymean(~Household_Income, Ethiopia_Design, na.rm= TRUE))
Household_Income_conf_ET <- confint(svymean(~Household_Income, Ethiopia_Design, na.rm= TRUE))
Household_Income_frame_ET <- data.frame(estimate = Household_Income_est_ET, 
                        CI = Household_Income_conf_ET)
Household_Income_frame_ET <- Household_Income_frame_ET*100
Household_Income_frame_ET$estimate.mean <- round(Household_Income_frame_ET$estimate.mean, 1)
Household_Income_est_labs <- c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%")
Household_Income_frame_ET <- cbind(Household_Income_frame_ET, Household_Income_est_labs)
Household_Income_frame_ET$Household_Income_est_labs <- factor(Household_Income_frame_ET$Household_Income_est_labs, level = c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%"))
levels(Household_Income_frame_ET$Household_Income_est_labs) <- gsub(" ", "\n", levels(Household_Income_frame_ET$Household_Income_est_labs))

Household_Incomeplot_ET <- ggplot(Household_Income_frame_CH,
       aes(x=Household_Income_est_labs, y=estimate.mean)) +
       geom_col(fill="honeydew2")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Income")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Household_Incomeplot_ET)
```
Vaccination
```{r}
svymean(~Q28, Ethiopia_Design, na.rm= TRUE)
confint(svymean(~Q28, Ethiopia_Design, na.rm= TRUE))
```
Put plots together 
```{r}
ET_plots <- multiplot(Ageplot_ET, Genderplot_ET, Educationplot_ET, Urban_Ruralplot_ET, Household_Incomeplot_ET, cols=2)
```
## Philippines
How many total respondents 
```{r}
nrow(filter(WGM_an, WP5 == "Philippines"))
```
How many respondents in country who have children and know about vaccines
```{r}
nrow(filter(WGM_an, WP5 == "Philippines" & Q27 == "Yes" & Q23 == "Yes"))
```
Filter survey weights to country
```{r}
PH_Design <- subset(WGM_anSurveyDesign, 
                        WP5 == "Philippines" &
                        Q27 == "Yes" &
                        Q23 == "Yes"
                        )
```
Age 
```{r}
Age_est_PH <- data.frame(svymean(~AgeCategories, PH_Design, na.rm= TRUE))
Age_conf_PH <- confint(svymean(~AgeCategories, PH_Design, na.rm= TRUE))
Age_frame_PH <- data.frame(estimate = Age_est_PH, 
                        CI = Age_conf_PH)
Age_frame_PH <- Age_frame_PH*100
Age_frame_PH$estimate.mean <- round(Age_frame_PH$estimate.mean, 1)
Age_est_labs <- c("15-29", "30-49", "50+")
Age_frame_PH <- cbind(Age_frame_PH, Age_est_labs)

Ageplot_PH <- ggplot(Age_frame_PH,
       aes(x=Age_est_labs, y=estimate.mean)) +
       geom_col(fill="gray78")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Age Cohort")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Ageplot_PH)
```
Gender
```{r}
Gender_est_PH <- data.frame(svymean(~Gender, PH_Design, na.rm= TRUE))
Gender_conf_PH <- confint(svymean(~Gender, PH_Design, na.rm= TRUE))
Gender_frame_PH <- data.frame(estimate = Gender_est_PH, CI = Gender_conf_PH)
Gender_frame_PH <- Gender_frame_PH*100
Gender_frame_PH$estimate.mean <- round(Gender_frame_PH$estimate.mean, 1)
Gender_est_labs <- c("Male", "Female")
Gender_frame_PH <- cbind(Gender_frame_PH, Gender_est_labs)

Genderplot_PH <- ggplot(Gender_frame_PH,
       aes(x=Gender_est_labs, y=estimate.mean)) +
       geom_col(fill="gray78")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Gender")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Genderplot_PH)
```
Education
```{r}
Education_est_PH <- data.frame(svymean(~Education, PH_Design, na.rm= TRUE))
Education_conf_PH <- confint(svymean(~Education, PH_Design, na.rm= TRUE))
Education_frame_PH <- data.frame(estimate = Education_est_PH, 
                        CI = Education_conf_PH)
Education_frame_PH <- Education_frame_PH*100
Education_frame_PH$estimate.mean <- round(Education_frame_PH$estimate.mean, 1)
Education_est_labs <- c("Primary", "Secondary", "Tertiary")
Education_frame_PH <- cbind(Education_frame_PH, Education_est_labs)

Educationplot_PH <- ggplot(Education_frame_PH,
       aes(x=Education_est_labs, y=estimate.mean)) +
       geom_col(fill="gray78")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), 
            position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ylim(0,100)+
  ggtitle("Education")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Educationplot_PH)
```
Setting 
```{r}
Urban_Rural_est_PH <- data.frame(svymean(~Urban_Rural, PH_Design, na.rm= TRUE))
Urban_Rural_conf_PH <- confint(svymean(~Urban_Rural, PH_Design, na.rm= TRUE))
Urban_Rural_frame_PH <- data.frame(estimate = Urban_Rural_est_PH, 
                        CI = Urban_Rural_conf_PH)
Urban_Rural_frame_PH <- Urban_Rural_frame_PH*100
Urban_Rural_frame_PH$estimate.mean <- round(Urban_Rural_frame_PH$estimate.mean, 1)
Urban_Rural_est_labs <- c("Rural or small town", "City or suburb")
Urban_Rural_frame_PH <- cbind(Urban_Rural_frame_PH, Urban_Rural_est_labs)

Urban_Ruralplot_PH <- ggplot(Urban_Rural_frame_PH,
       aes(x=Urban_Rural_est_labs, y=estimate.mean)) +
       geom_col(fill="gray78")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean),  position = position_dodge(width = 1),
            vjust = -1,
            size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Setting")+
  theme_classic()+
  ylim(0,100)+
  theme(plot.title = element_text(size = 12))
print(Urban_Ruralplot_PH)
```
Income
```{r}
Household_Income_est_PH <- data.frame(svymean(~Household_Income, PH_Design, na.rm= TRUE))
Household_Income_conf_PH <- confint(svymean(~Household_Income, PH_Design, na.rm= TRUE))
Household_Income_frame_PH <- data.frame(estimate = Household_Income_est_PH, 
                        CI = Household_Income_conf_PH)
Household_Income_frame_PH <- Household_Income_frame_PH*100
Household_Income_frame_PH$estimate.mean <- round(Household_Income_frame_PH$estimate.mean, 1)
Household_Income_est_labs <- c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%")
Household_Income_frame_PH <- cbind(Household_Income_frame_PH, Household_Income_est_labs)
Household_Income_frame_PH$Household_Income_est_labs <- factor(Household_Income_frame_PH$Household_Income_est_labs, level = c("Poorest 20%", "Second 20%", "Middle 20%", "Fourth 20%", "Top 20%"))
levels(Household_Income_frame_PH$Household_Income_est_labs) <- gsub(" ", "\n", levels(Household_Income_frame_PH$Household_Income_est_labs))

Household_Incomeplot_PH <- ggplot(Household_Income_frame_PH,
       aes(x=Household_Income_est_labs, y=estimate.mean)) +
       geom_col(fill="gray78")+
  geom_errorbar(aes(ymin=CI.2.5.., ymax=CI.97.5..), width = .2)+ 
  geom_text(aes(label=estimate.mean), nudge_y = -10, size=3)+ 
  labs(y=" ", x=" ")+
  ggtitle("Income")+
  theme_classic()+
  theme(plot.title = element_text(size = 12))
print(Household_Incomeplot_PH)
```
Vaccination
```{r}
svymean(~Q28, PH_Design, na.rm= TRUE)
confint(svymean(~Q28, PH_Design, na.rm= TRUE))
```
Put plots together 
```{r}
PH_plots <- multiplot(Ageplot_PH, Genderplot_PH, Educationplot_PH, Urban_Ruralplot_PH, Household_Incomeplot_PH, cols=2)
```




















